---
title: "Artifact Travelogue Demo"
author: "Cody Micah Carmichael, MPH, CPH"
date: "5/28/2022"
output: html_document
---
```{r setup, include=FALSE}
#uncomment line below if needed.
#install.packages('leaflet')
library(leaflet)

```
```{r functions, include=FALSE}


#Creates a standardized data frame. Can be replaced if needed.
#May want to add a functionality for "years of ownership_start and _end, e.g. 1808, 2022, so that way we can sort entries based on that. 
create_dataframe = function(Name="Empty_For_Now", ImageLink="Empty_For_Now",
                            OwnName="Empty_For_Now", OwnDuration_years="Empty_For_Now",
                            OwnLoc="Empty_For_Now", OwnLat="Empty_For_Now",
                            OwnLong="Empty_For_Now", DescUpdate="Empty_For_Now", 
                            Origin="Empty_For_Now", OriginLat="Empty_For_Now", 
                            OriginLong="Empty_For_Now", Notes="Empty_For_Now"){
  
  Art_DF <- data.frame(Name, ImageLink, OwnName, OwnDuration_years, OwnLoc, OwnLat, OwnLong, DescUpdate, Origin, OriginLat, OriginLong, Notes )
}


#Can add additional rows manually, but also can be hooked onto a CSV read, interactive doc, etc, or left out for main create function.
add_row_to_entry = function(Art_DF ,
                            OwnName="Empty_For_Now", OwnDuration_years="Empty_For_Now",
                            OwnLoc="Empty_For_Now", OwnLat="Empty_For_Now",
                            OwnLong="Empty_For_Now", DescUpdate="Empty_For_Now", 
                            Notes="Empty_For_Now"){
  Name=Art_DF$Name[1]
  ImageLink=Art_DF$ImageLink[1]
  Origin = Art_DF$Origin[1]
  OriginLat= Art_DF$OriginLat[1]
  OriginLong=Art_DF$OriginLong[1]
  
  
  
  
  Art_DF2 <- data.frame(Name, ImageLink, OwnName, OwnDuration_years, OwnLoc, OwnLat, OwnLong, DescUpdate, Origin, OriginLat, OriginLong, Notes )
  
  Extended_Art_DF = rbind(Art_DF, Art_DF2)
}





#function that uses leaflet to create map. We can create more complex popups (length of stay, previous owner, etc), this is just a tech demo. 

create_map = function(Art_DF){
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=Art_DF$OwnLong, lat=Art_DF$OwnLat, popup= Art_DF$OwnName) %>%
    addCircles(lng=Art_DF$OriginLong[1], lat=Art_DF$OriginLat[1], popup= paste("Origin:",Art_DF$Origin[1]), color = "Orange")
  
  # Print the map


  return(m)
  
}

```
```{r tester_df, include=FALSE}

#We can automate this according to R's work. 
Rosetta_DF = create_dataframe(Name="Rosetta Stone",
                              #change image link with proper path as needed, or we can use relative paths later. 
                              ImageLink="/Artifact-Travelogues-/The Rosetta Stone/rosettastone.jpg",
                              OwnName="The British Museum", OwnDuration_years=220, OwnLoc="London, England", OwnLat=51.519466,
                              OwnLong=-0.1268406, Origin="Memphis, Egypt", OriginLat = 29.844722, OriginLong = 31.250833,
                              Notes="The Rosetta Stone features writing in Greek, Latin, and Egyptian.")




Rosetta_DF <- add_row_to_entry(Rosetta_DF, OwnName = "Rochester Fake Museum", OwnLoc = "Rochester, New York", OwnDuration_years = 3, OwnLat = 43.161030, OwnLong = -77.610924  )





Rosetta_Map <- create_map(Rosetta_DF)




## Can automate text generation below through a loop, but this is just to make sure it matches expectations
```


# `r Rosetta_DF$Name[1]` Entry


## **Artifact Name: `r Rosetta_DF$Name[1]`**


![Image of `r Rosetta_DF$Name[1]` ](`r Rosetta_DF$ImageLink[1]`)


## Note 1

### Current owner(s): `r Rosetta_DF$OwnName[1]`

Owner Location: `r Rosetta_DF$OwnLoc[1]`

Duration of Ownership (years): `r Rosetta_DF$OwnDuration_years[1]` 

Notes: `r Rosetta_DF$Notes[1]`


## Note 2:

### Previous owner(s): `r Rosetta_DF$OwnName[2]`

Owner Location: `r Rosetta_DF$OwnLoc[2]`

Duration of Ownership (years): `r Rosetta_DF$OwnDuration_years[2]`






## Map of Locations which held Artifact: `r Rosetta_DF$Name[1]`


`r Rosetta_Map`